Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-20 main.tex
Added table of bicycle physical parameters as an appendix, fixes #13.

>>>>

\section*{Appendix}
%
Physical parameters and estimated uncertainty (standard deviation) for the
balance assist bicycle without and with the rider. These are derived from the
measurement approach in \citet{Moore2012}. Variable names match the notation
from the benchmark bicycle model presented in \citet{Meijaard2007}.

\begin{tabular}{llrrrr}
  \toprule
  Variable & Unit & Without Rider & Uncertainty & With Rider & Uncertainty \\
  \midrule
  \(c\) & \si{\meter} & 0.04 & 0.01 & 0.04 & 0.01 \\
  \(g\) & \si{\meter\per\second\squared} & 9.80665 & NA & 9.80665 & NA \\
  \(I_{Bxx}\) & \si{\kilogram\meter\squared} & 1.12 & 0.02 & 19.7 & 0.3 \\
  \(I_{Bxz}\) & \si{\kilogram\meter\squared} & 0.05 & 0.03 & -3.5 & 0.2 \\
  \(I_{Byy}\) & \si{\kilogram\meter\squared} & 3.16 & 0.08 & 22.7 & 0.4 \\
  \(I_{Bzz}\) & \si{\kilogram\meter\squared} & 2.12 & 0.03 & 5.0 & 0.1 \\
  \(I_{Fxx}\) & \si{\kilogram\meter\squared} & 0.0995 & 0.0005 & 0.0995 & 0.0005 \\
  \(I_{Fyy}\) & \si{\kilogram\meter\squared} & 0.1902 & 0.0009 & 0.1902 & 0.0009 \\
  \(I_{Hxx}\) & \si{\kilogram\meter\squared} & 0.298 & 0.003 & 0.298 & 0.003 \\
  \(I_{Hxz}\) & \si{\kilogram\meter\squared} & -0.038 & 0.007 & -0.038 & 0.007 \\
  \(I_{Hyy}\) & \si{\kilogram\meter\squared} & 0.257 & 0.006 & 0.257 & 0.006 \\
  \(I_{Hzz}\) & \si{\kilogram\meter\squared} & 0.057 & 0.003 & 0.057 & 0.003 \\
  \(I_{Rxx}\) & \si{\kilogram\meter\squared} & 0.1023 & 0.0006 & 0.1023 & 0.0006 \\
  \(I_{Ryy}\) & \si{\kilogram\meter\squared}& 0.1887 & 0.0007 & 0.1887 & 0.0007 \\
  \(\lambda\) & \si{\radian} & 0.25 & 0.03 & 0.25 & 0.03 \\
  \(m_B\) & \si{\kilogram} & 22.50 & 0.01 & 106.00 & 0.01 \\
  \(m_F\) & \si{\kilogram} & 2.23 & 0.01 & 2.23 & 0.01 \\
  \(m_H\) & \si{\kilogram} & 4.30 & 0.01 & 4.30 & 0.01 \\
  \(m_R\) & \si{\kilogram} & 4.08 & 0.01 & 4.08 & 0.01 \\
  \(r_F\) & \si{\meter} & 0.3523 & 0.0001 & 0.3523 & 0.0001 \\
  \(r_R\) & \si{\meter} & 0.3489 & 0.0001 & 0.3489 & 0.0001 \\
  \(w\) & \si{\meter} & 1.113 & 0.008 & 1.113 & 0.008 \\
  \(x_B\) & \si{\meter} & 0.52 & 0.01 & 0.374 & 0.002 \\
  \(x_H\) & \si{\meter} & 0.92 & 0.02 & 0.92 & 0.02 \\
  \(z_B\) & \si{\meter} & -0.52 & 0.02 & -1.009 & 0.003 \\
  \(z_H\) & \si{\meter} & -0.860 & 0.006 & -0.860 & 0.006 \\
  \bottomrule
\end{tabular}
